\huge A Usability Evaluation of Tor Launcher

### 2016-11-15 pets2017-paper/pets2017-paper.tex
unmark things to filter out P93 until I'm sure I should do it

Of our recruited 124 participants, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Results} 
124 people participated in our experiment, but we used data from 113. We filtered participants who made errors in completing the consent form, did not complete the exit survey, did not understand the task, or did not interact with the instrumented interface. In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}). Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
{\color {red}
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08, 
the maximum time a participant took to finish the task.
}
}
\label{table:participant-summary}
\end{table}

\label{all-participant-edges} 
\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
{\color {red}
A summary of our valid participants' paths through the interface.
The length of the bars show the total time taken to complete the task,
except for those we cut off after approximately 40 minutes.
Different colors indicate which screen they were on during the experiment.
If participants were doing other things (i.e. searching for help in another browser)
while off-focus, this time still counts as spending time in that off-focus window. 
``Not running'' are times when Tor Launcher was closed (
i.e. restarting the application).}
}
\label{fig:all-participant-edges}
\end{figure*}

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
{\color {red}
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
Most successful E3 participants
used meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

% failure observations
{\color {red} 17\% (19 of 114) of participants were not able to successfully connect to Tor. Five (P73, P75, P89, P91, P106, P110) tried a direct connection. When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies. Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor. We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails. Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed. Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder. We suspect that they would have succeeded if they had gotten a response.}

%success rate and version
{\color {red} Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).} That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

@@

%time observations (how long people took)
The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time {\color {red} (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).} Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.

%time to success and version
{\color {red} Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).} That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
{\color {red}
The dots show the raw connection times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' (did not finish) numbers at the right show how many of participants 
did not finish, who were assigned the maximum time of 40:08.}
}
\label{fig:time_to_success_clamped}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
{\color {red}
Cumulative success rates over time, shown continuously and at discrete times we found interesting.
Notice that the longer the time went on, participants were less likely to succeed. 
At 1.5 minutes, every E1-NEW participant had finished,
but only 58\% of E1-OLD had finished by that time.  
At 10 minutes, most participants in E2 had finished. }
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

%configuration time and version
{Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).} That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

\begin{table}[t]
\centering
\input{median_time.tex}
\caption{
{\color {red}
The median percent of time spent on each screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.}
} 
\label{table:median_time}
\end{table}

>>>>

124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface. Of the 114, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Results} 
We summarize what our participants did below.  Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment. In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08, 
the maximum time a participant took to finish the task.
}
\label{table:participant-summary}
\end{table}

\label{all-participant-edges} 
\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
A summary of our valid participants' paths through the interface.
The length of the bars show the total time taken to complete the task,
except for those we cut off after approximately 40 minutes.
Different colors indicate which screen they were on during the experiment.
If participants were doing other things (i.e. searching for help in another browser)
while off-focus, this time still counts as spending time in that off-focus window. 
``Not running'' are times when Tor Launcher was closed (
i.e. restarting the application).}
\label{fig:all-participant-edges}
\end{figure*}

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
Most successful E3 participants
used meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

% failure observations
17\% (19 of 114) of participants were not able to successfully connect to Tor. Five (P73, P75, P89, P91, P106, P110) tried a direct connection. When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies. Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor. We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails. Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed. Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder. We suspect that they would have succeeded if they had gotten a response.

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

@@

%time observations (how long people took)
The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.

%time to success and version
Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$). That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
The dots show the raw connection times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' (did not finish) numbers at the right show how many of participants 
did not finish, who were assigned the maximum time of 40:08.}
\label{fig:time_to_success_clamped}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, shown continuously and at discrete times we found interesting.
Notice that the longer the time went on, participants were less likely to succeed. 
At 1.5 minutes, every E1-NEW participant had finished,
but only 58\% of E1-OLD had finished by that time.  
At 10 minutes, most participants in E2 had finished. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

%configuration time and version
Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$). That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

\begin{table}[t]
\centering
\input{median_time.tex}
\caption{
The median percent of time spent on each screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.}
\label{table:median_time}
\end{table}
